### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@b4859b66321cb2a8375edc04f836d83e592252ff 🚀

\hypertarget{the-metaweb-embeds-strong-ecological-hypotheses}{%
\section{The metaweb embeds strong ecological
hypotheses}\label{the-metaweb-embeds-strong-ecological-hypotheses}}

>>>>

\hypertarget{the-metaweb-embeds-ecological-hypotheses-and-practices}{%
\section{The metaweb embeds ecological hypotheses and
practices}\label{the-metaweb-embeds-ecological-hypotheses-and-practices}}
